Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-20 paper/ijm.tex
hint to inactivity removed in 3.1

We limit ourselves to men and women in the main working age, between 25 and
55 years old.  Further, we only analyse
individuals who are either working or actively looking for a job.

The dataset allows us to control for standard personal
characteristics and human capital variables, such as age, education
and family status.  The central variables in this study are the same
as in \citep{Leping2008}:

@@

The labor market outcomes we analyze are income, the ``last salary on the main job'' and
labor force status (working, unemployed or inactive).

The survey includes self-reported language skills on languages used at
home, and all other languages they understand.  The respondents are
give some guidance in assessing their skills, they can report either
no knowledge, understanding, speaking, writing, or using the
language at home.  We consolidate this information into a dummy variable, equal
to one if one speaks or writes, or uses that language at
home, and zero otherwise.  Hence we disregard passive understanding
only.
  The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
1995 are partly based on extrapolation, assuming individual language
skills did not vary before that date.

For further evidence on ethnic and gender segregation at workplace we use data
from 2008 Integration Monitor Survey.  The survey was conducted by
SaarPoll and focuses on
ethnic relations in Estonia.  The sample size is 1500,
500 of the respondents consider themselves not ethnic Estonians.  We analyse
two questions: ``which is the language of communication at your
workplace?'' and ``which languages do you need at work''.  The first
question addresses the ethnic segregation while the second focuses on
the need of communication.

>>>>

We limit ourselves to men and women in the main working age, between 25 and
55 years old.  Further, we only analyse
individuals who are either working or actively looking for a job.
The dataset allows us to control for standard personal
characteristics and human capital variables, such as age, education
and family status.  The central variables in this study are the same
as in \citet{Leping2008}.

@@

The labor market outcomes we analyze are income, the ``last salary on the main job'', and
labor force status (working or unemployed).

The survey includes self-reported language skills on all languages
respondents can understand or communicate.  The questionnaire 
gives some guidance in assessing the skills, one can report either
no knowledge, understanding, speaking, writing, or using the
language at home.  We consolidate this information into a dummy variable, equal
to one if one speaks or writes, or uses that language at
home, and zero otherwise.  Hence we disregard passive understanding
only.
  The reader should keep in mind that while the pre-2000 waves include retrospective income, they do not include retrospective language skills. In this way, the results before
1995 are partly based on extrapolation, assuming individual language
skills did not vary before that date.

For further evidence on ethnic and gender segregation at workplace we use data
from 2008 Integration Monitor Survey.  The survey was conducted by
SaarPoll and focuses on
ethnic relations in Estonia.  The sample size is 1500, out of which 
500 respondents do not consider themselves ethnic Estonians.  We analyse
two questions: ``which is the language of communication at your
workplace?'' and ``which languages do you need at work''.  The first
question addresses the ethnic segregation while the second focuses on
the need of communication.
